A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex

Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that it has a diverse worker population that should represent a wide variety of languages.

>>>>

Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'. A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs. Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them. Worker identities remain anonymous to requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accept tasks. 
Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that it has a diverse worker population that should represent a wide variety of languages.
